---
title: "Exploratory Data Analysis"
author: "STOR 320.(01 OR 02) Group PLACE_GROUP_NUMBER_HERE (Ex: STOR 320.01 Group 12)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

# Import Data Below
# read_csv()
dt = read_csv('Placement_Data_Full_Class.csv')
```

# Creator: FIRSTNAME LASTNAME

### Q1: WRITE_QUESTION_HERE

```{r}
#
```

### Q2: WRITE_QUESTION_HERE

```{r}
#
```

# Interpreter: Yunzhou Liu

### Q1: Is there a correlation between employability test and salary?

```{r}
#
# Need to first drop the NAs
# Test for correlation
wo.NA = dt %>% filter(!is.na(etest_p) & !is.na(salary))
cor(wo.NA$etest_p, wo.NA$salary)
wo.NA %>% ggplot(mapping=aes(x=etest_p, y=salary))+geom_point()+geom_smooth()
```

The `cor` output gives us the correlation between `employability test` and `salary`, which is `r cor(wo.NA$etest_p, wo.NA$salary)`. And thus we can see that there is a **weak positive correlation** between `employability test` and `salary`. 

### Q2: Are there any significant differences of salaries between different fields of undergraduate research?

```{r}
wo.NA2 = dt %>% filter(!is.na(degree_t) & !is.na(salary))
wo.NA2 %>% ggplot(mapping=aes(x=degree_t, y=salary))+geom_boxplot()+geom_point(data=wo.NA2 %>% group_by(degree_t) %>% summarise(deg.mean = mean(salary)) %>% ungroup(), mapping=aes(x=degree_t, y=deg.mean, color='red'))
TukeyHSD(aov(salary~degree_t, data=wo.NA2))
```

From the boxplot above, we can assume that there is not a significant differences of salaries between different fields of undergraduate research. 
And we propose our Null and Alternative Hypotheses: 

- Null Hypothesis $H_{0, i, j}$: There is **no difference** in mean between two groups of different field of undergraduate research for any two groups ${i, j}$
- Alternative Hypothesis $H_{A, i, j}$: There is **at least one group** with mean significantly different from another group. 

We can see from the Tukey HSD test above that all of these adjusted p-values are larger than 5%, which means that we reject our alternative hypothesis, and there **isn't a significant difference in salary between different field of study**.

# Orator: Camryn Blawas

### Q1: Do secondary education percentage and higher secondary education percentage have an effect on job placement ?

```{r}
SE_Data = select(PlacementData, "SE_Grade", "JobStatus")
SE_Data = mutate(SE_Data, Year = ifelse(is.na(SE_Grade), NA, "SE_Grade"), Grade = SE_Grade)
SE_Data1 = select(SE_Data, "Grade", "JobStatus", "Year")
HSE_Data = select(PlacementData, "HSE_Grade", "JobStatus")
HSE_Data = mutate(HSE_Data, Year = ifelse(is.na(HSE_Grade), NA, "HSE_Grade"), Grade = HSE_Grade)
HSE_Data1 = select(HSE_Data, "Grade", "JobStatus", "Year")
All_Grades = rbind(SE_Data1, HSE_Data1)
ggplot(All_Grades)+
  geom_lv(aes(x=JobStatus, y=Grade, fill=Year))
```

### Q2: What is the effect of undergraduate degree type and MBA specialization on salary?

```{r}
SciTechUG_MktFinMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
SciTechUG_MktFinMBA = mutate(SciTechUG_MktFinMBA, Special = ifelse(UG_Specialization == "Sci&Tech" & MBA_Specialization == "Mkt&Fin","SciTechUG_MktFinMBA", NA))
SciTechUG_MktHRMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
SciTechUG_MktHRMBA = mutate(SciTechUG_MktHRMBA, Special = ifelse(UG_Specialization == "Sci&Tech" & MBA_Specialization == "Mkt&HR","SciTechUG_MktHRMBA", NA))
CommMgmtUG_MktFinMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
CommMgmtUG_MktFinMBA = mutate(CommMgmtUG_MktFinMBA, Special = ifelse(UG_Specialization == "Comm&Mgmt" & MBA_Specialization == "Mkt&Fin","CommMgmtUG_MktFinMBA", NA))
CommMgmtUG_MktHRMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
CommMgmtUG_MktHRMBA = mutate(CommMgmtUG_MktHRMBA, Special = ifelse(UG_Specialization == "Comm&Mgmt" & MBA_Specialization == "Mkt&HR","CommMgmtUG_MktHRMBA", NA))
OtherUG_MktFinMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
OtherUG_MktFinMBA = mutate(OtherUG_MktFinMBA, Special = ifelse(UG_Specialization == "Others" & MBA_Specialization == "Mkt&Fin","OtherUG_MktFinMBA", NA))
OtherUG_MktHRMBA = select(PlacementData, UG_Specialization, MBA_Specialization, Salary)
OtherUG_MktHRMBA = mutate(CommMgmtUG_MktHRMBA, Special = ifelse(UG_Specialization == "Others" & MBA_Specialization == "Mkt&HR","OtherUG_MktHRMBA", NA))
Q8Data= rbind(SciTechUG_MktFinMBA, SciTechUG_MktHRMBA, CommMgmtUG_MktFinMBA, CommMgmtUG_MktHRMBA, OtherUG_MktFinMBA, OtherUG_MktHRMBA)
Q8Data1 = na.omit(Q8Data)
ggplot(Q8Data1)+
  geom_lv(aes(x=Special, y=Salary))+
  coord_flip()
```

# Deliverer: FIRSTNAME LASTNAME

### Q1: WRITE_QUESTION_HERE

```{r}
#
```

### Q2: WRITE_QUESTION_HERE

```{r}
#
```

# Follow-up Questions

### New Questions Based Off Initial Investigation

- Q1: WRITE_QUESTION_HERE
- Q2: WRITE_QUESTION_HERE
- Q3: WRITE_QUESTION_HERE 
- Q4: WRITE_QUESTION_HERE

### Investigation of Follow-up Questions

GIVE WHAT 2 QUESTIONS YOU ATTEMPTED TO INVESTIGATE FURTHER IN COMPLETE SENTENCES (*Example:* Our group decided to investigate Q2 and Q4 in further detail.)

SHOW AT LEAST 2 TABLES OR FIGURES BELOW THAT EXPLORE ANSWERS FOR THE QUESTIONS YOU ARE INVESTIGATING FURTHER.

```{r}
#
```

```{r}
#
```

# Summary

GIVE A 2 PARAGRAPH SUMMARY. 

PARAGRAPH 1 SHOULD DESCRIBE WHAT YOU LEARNED ABOUT YOUR DATA FROM INVESTIGATING THE INITIAL QUESTIONS. DID YOU FIND ANYTHING UNUSUAL IN YOUR DATA? DID ANYTHING SURPRISE YOU? WHICH OF THE INITIAL QUESTIONS WERE HELPFUL IN LEADING YOU TO MORE QUESTIONS?

PARAGRAPH 2 SHOULD SUMMARIZE WHAT YOU LEARNED FROM INVESTIGATING THE FOLLOW-UP QUESTIONS. WHY ARE THESE FOLLOW-UP QUESTIONS INTERESTING FOR INVESTIGATION? DESCRIBE THE TABLES/FIGURES YOU USED TO EXPLORE ANSWERS TO THESE FOLLOW-UP QUESTIONS? WHAT DID YOU LEARN FROM THE TABLES/FIGURES REGARDING THE FOLLOW-UP QUESTIONS YOU PROPOSED?















